A Large-Area, Spatially Continuous Assessment of Land Cover Map Error and Its Impact on Downstream Analyses

### 2017-09-05 inst/paper/main.tex
Redid c9 to double-check some SI values (0 production bias in agricultural area version). It was fine--confirmed with checks 1051-1071. Updated package.

>>>>

\section*{Supporting information}
Additional information on supplemental methods and results can be found in the Supplementary Methods and Results document. Additionally, the paper, code, and all non-proprietary data are available as an installable R package at https://github.com/agroimpacts/croplandbias.
